---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r warning=FALSE, include=}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nycrime

<!-- badges: start -->
<!-- badges: end -->

This package is designed to get the data from 2019 NYC Arrest Data according different tasks. It can allow you to make requests for more
information about this data set.

## Installation

You can install the released version of nycrime from [NYCRIME]()

``` {}
# install.package("devtools")
# library("devtools")
devtools::install_github("Shuhe-Ma/PAC/nycrime")
```

## The First Function

Please register and get your API key from [NYC Open Data](https://data.cityofnewyork.us/signup)

Then paste the unique APP Token and run the first function called `my_api_key` and restart R before you complete other tasks.

```{}
# my_api_key("YOUR KEY")
# .rs.restartR()
```


## Example

This is a basic example which shows you how to get the raw data:

```{r}
library(nycrime)
```

crime_type_add(200, "M", "M")

```{r get raw data, echo=FALSE, warning=FALSE}
crime_type_add <- function(limit_num = 5000000, crime_type = "M", region="M") {
endpoint <- "https://data.cityofnewyork.us/resource/uip8-fykc.csv"
query2 <- list("$$app_token" = Sys.getenv("NYC_API_KEY"), "$limit" = paste(limit_num), "law_cat_cd" = paste(crime_type), "arrest_boro"=paste(region))
get <- GET(endpoint, query = query2)
if (http_error(get)) {
	warning("The request produced an error.")
} else {
	data1 <- as.data.frame(content(get))
}
data1 < data1 %>% filter(law_cat_cd == paste(crime_type), arrest_boro == paste(region))

data1

}
crime_type_add(200, "M", "M")
```


