---
title: "NYCRIME Vignette"
author: "Shuhe Ma"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(knitr)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(tidyr)
library(purrr)
library(plyr)
library(stringr)
library(httr)
library(nycrime)
```

```{r setup}
knitr::opts_chunk$set(include = FALSE)
library(nycrime)
```
# NYCRIME Package
This package is designed to get the data from 2019 NYC Arrest Data according different tasks. It can allow you to make requests for more
information about this data set.

## Function Description:

```{}
`my_api_key(your_API)`: Let the users enter their own API key and store it for the future uses.
```
- your_API: The API key you get from NYC open data

```{}
getRawData(limit_num):  Get the raw data set, please set your own APP token and the size of your data.
```
- limit_num: how many observations you want to get.

```{}
getCleanData(limit_num): The user has an option to get data in a simpler version. The data will contain fewer columns with readable names.
```
- limit_num: how many observations you want to get.

```{}
crime_type_add(limit_num, crime_type, region): Get the number of crimes based on their types and location
```
- limit_num: how many observations you want to get.
- crime_type: the specific crime type. ("F" = "Felony",  "V", "Violence", "M", "Misdemeanor")
- region: the specific region in NYC. ("M"= "Manhattan", "B"= "Bronx", "S"= "Staten Island","Q" = "Queens", "K"= "Brooklyn")

```{}
crime_in_date(limit_num, month, day): Get the crimes based on the date
```
- limit_num: how many observations you want to get.
- month: month number from 01 - 09.
- day; day number from 01 - 31.

```{}
crime_type_gen(gender): Get the summary table for the gender based on the crime types.
```
- gender: "M", "F" or "all".

```{}
crime_daily(month): Daily crime in one month.
```
- month: month number: 01 - 09.

```{}
crime_trend(month):  Trend in one month
```
- month: month number: 01 - 09.

```{}
crime_desc <- function(desc="ROBBERY"): Show Crimes based on descriptions by age group.
```
- desc: desciption of criminal behaviors: "ROBBERY", "ASSAULT" ...
